Title Goes Here

### 2020-04-02 analysis/paper/paper.Rmd
added phase for the SPs

@@

#list of all attributes
df <- data.frame(ML, BL, TL, SL, MW, TW, SW, files)

@@

autoplot(prcomp(DF), data = df_sitename, colour = 'sitename')

ggbiplot(PCA, obs.scale = 1, var.scale = 1,          ellipse = TRUE, circle = TRUE)+
scale_color_discrete (name = '') + groups (df$files)
  theme(legend.direction = 'horizontal', legend.position = 'top')

@@

#using ggfortify package
library(ggfortify) 
autoplot(prcomp(DF))

>>>>

#getting info for phase of each site
SPstage <- read.csv(here("analysis/data/SPstage.csv"))

@@

#list of all attributes
df <- data.frame(ML, BL, TL, SL, MW, TW, SW, files, SPstage$Stage)

@@

library(ggfortify) 
autoplot(prcomp(DF), data = df_sitename, colour = 'SPstage.Stage')

@@
